
```{r}
library(dplyr)
library(stringr)
library(tidyverse)
```


This code should prepare two data files. Both data files are cleaning data, so it only contains letters and each query is a single word. One file has queries with their frequency, and the other only has queris but allow for duplicate, i.e. how you will see the data in the real world.



```{r}
create_query_with_freq <- function(datafile, outputfile){
  data <- read.csv(datafile, header = TRUE, sep = ',')
  
  test2 <- data.frame(table(data$Query))
  colnames(test2) <- c("query", "frequency")
  
  #clean data
  test2$query <- str_replace_all(test2$query, "[:punct:]", "")
  test2$query <- str_replace_all(test2$query, "www", "")
  test2$query <- str_replace_all(test2$query, ".com", "")
  test2$query <- str_replace_all(test2$query, "[^a-zA-Z -]", "")
  
  #Remove empty rows
  entries <- which(nzchar(test2$query)==TRUE)  # non-empty rows
  test2 <- test2[entries, ]  # keep only non-empty rows
  
  training_data <-  test2 %>% separate_rows(query)
  training_data$query <- trimws(training_data$query)

  entries <- which(nzchar(training_data$query)==TRUE)  # non-empty rows
  

  training_data <- training_data[entries, ]  # keep only non-empty rows

  training_data2 <- training_data %>% group_by(query) %>% summarise(frequency = sum(frequency))

  
  print(length(training_data2$query))
  print(sum(training_data2$frequency))
  write.csv(training_data2, outputfile, row.names = FALSE)
  return(training_data2)
}
```

```{r}
experiment_data_with_freq <-  create_query_with_freq("../ProcessedData/raw_data_03_25_to_04_25.csv", "../ProcessedData/experiment_data_03_25_to_04_25_clean_words_with_freq.csv" )
```


##### Create query train

input file = "../ProcessedData/raw_data_03_25.csv"

output file = "../ProcessedData/experiment_data_03_25_clean_words_no_freq.csv"

```{r}
create_query_no_freq <- function(datafile, outputfile) {
  test2 <- read.csv(datafile, header = TRUE, sep = ',')
  test2 <- test2[,c("AnonID", "Query")]
  colnames(test2) <- c("id", "query")
  
  test2$query <- str_replace_all(test2$query, "[:punct:]", "")
  test2$query <- str_replace_all(test2$query, "www", "")
  test2$query <- str_replace_all(test2$query, ".com", "")
  test2$query <- str_replace_all(test2$query, "[^a-zA-Z -]", "")
  
  entries <- which(nzchar(test2$query)==TRUE)  # non-empty rows
  test2 <- test2[entries, ]  # keep only non-empty rows
  
  training_data <-  test2 %>% separate_rows(query)
  training_data$query <- trimws(training_data$query)
  entries <- which(nzchar(training_data$query)==TRUE)  # non-empty rows
  training_data <- training_data[entries, ]  # keep only non-empty rows
  training_data <- training_data$query

  write.csv(training_data, outputfile, row.names = FALSE)
  print(length(training_data))
  return(data.frame(training_data))
}
```

```{r}
no_freq <- create_query_no_freq("../ProcessedData/raw_data_03_25_to_04_25.csv", "../ProcessedData/experiment_data_03_25_to_04_25_clean_words_no_freq.csv" )
```

